---
title: "Results of Replications of Darley et al (2000, Study 2)"
author: "Many Legal Labs"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file, encoding = encoding, output_dir = "./reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Run all necessary scripts

source("./scripts/simulate/darley_simulation.R") # REPLACE WITH DATA IMPORTATION
source("./scripts/wrangle/darley_prelim.R")
source("./scripts/calculate/darley_core.R")
source("./scripts/analyze/darley_analysis.R")

```

# Overview

# Hypothesis 1

Participants will recommend higher punishment when the perpetrator acted in a jealous rage, compared to when the behavior was caused by an inoperable tumor.

## Meta-analysis of Replications

This hypothesis will be tested using standardized mean differences for punishment recommendation, for jealous rage vs. inoperable tumor.

```{r}
darley_h1_meta
```

## Forest Plot

```{r}
darley_h1_forest
```

# Hypothesis 2

Participants will recommend higher punishment when the perpetrator acted in a jealous rage, compared to when the behavior was caused by an operable tumor.

## Meta-analysis of Replications

This hypothesis will be tested using standardized mean differences for punishment recommendation, for jealous rage vs. operable tumor.

```{r}
darley_h2_meta
```

## Forest Plot

```{r}
darley_h2_forest
```

# Hypothesis 3

Participants will recommend higher punishment when the perpetrator acted because of an inoperable tumor, compared to when the behavior was caused by an operable tumor.

## Meta-analysis of Replications

This hypothesis will be tested using standardized mean differences for punishment recommendation, for operable tumor vs. inoperable tumor

```{r}
darley_h3_meta
```

## Forest Plot

```{r}
darley_h3_forest
```

# Manipulation Check 1

Participants will attribute responsibility to the actor more frequently in the jealous rage condition, compared to when the behavior was caused by an inoperable tumor.

## Meta-analysis of Replications

We will assess this manipulation check with proportion differences (odds ratios) in attributing responsibility to the actor, for Scenario (jealous rage vs. inoperable and operable).

```{r}
darley_mc1_meta
```

## Forest Plot

```{r}
darley_mc1_forest
```

# Manipulation Check 2

Participants will attribute responsibility to the actor more frequently in the jealous rage condition, compared to when the behavior was caused by an inoperable tumor.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in attributing responsibility to the actor, for Scenario (jealous rage vs. operable).

```{r}
darley_mc2_meta
```

## Forest Plot

```{r}
darley_mc2_forest
```

# Manipulation Check 3

Participants will attribute responsibility to the actor more frequently in the inoperable tumor condition compared to the operable tumor condition.

Darley et al. found a nonsignificant difference for this comparison, but the direction of proportions was such that more people attributed responsibility to the actor when the tumor was inoperable.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in attributing responsibility to the actor, for Scenario (operable vs. inoperable).

```{r}
darley_mc3_meta
```

## Forest Plot

```{r}
darley_mc3_forest
```

# Manipulation Check 4

Participants in the jealous rage condition will recommend prison more frequently than those in the inoperable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (jealous rage vs. inoperable).

```{r}
darley_mc4_meta
```

## Forest Plot

```{r}
darley_mc4_forest
```

# Manipulation Check 5

Participants in the jealous rage condition will recommend prison more frequently than those in the operable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (jealous rage vs. operable).

```{r}
darley_mc5_meta
```

## Forest Plot

```{r}
darley_mc5_forest
```

# Manipulation Check 6

Participants in the operable tumor condition will recommend prison more frequently than those in the inoperable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (operable vs. inoperable).

```{r}
darley_mc6_meta
```

## Forest Plot

```{r}
darley_mc6_forest
```

# Manipulation Check 7

Participants in the inoperable tumor condition will recommend hospitalization more frequently than those in the jealous rage condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (jealous rage vs. inoperable).

```{r}
darley_mc7_meta
```

## Forest Plot

```{r}
darley_mc7_forest
```

# Manipulation Check 8

Participants in the operable tumor condition will recommend hospitalization more frequently than those in the jealous rage condition

This difference was nonsignificant in the original study, but directionally, more people in the operable tumor condition recommended hospitalization.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (jealous rage vs. operable).

```{r}
darley_mc8_meta
```

## Forest Plot

```{r}
darley_mc8_forest
```

# Manipulation Check 9

Participants in the operable tumor condition will recommend hospitalization more frequently than those in the inoperable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (operable vs. inoperable).

```{r}
darley_mc9_meta
```

## Forest Plot

```{r}
darley_mc9_forest
```

# Manipulation Check 10

Participants in the jealous rage condition will recommend release approximately equally compared to those in the inoperable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (jealous rage vs. inoperable).

```{r}
darley_mc10_meta
```

## Forest Plot

```{r}
darley_mc10_forest
```

# Manipulation Check 11

Participants in the jealous rage condition will recommend release less frequently compared to those in the operable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (jealous rage vs. operable).

```{r}
darley_mc11_meta
```

## Forest Plot

```{r}
darley_mc11_forest
```

# Manipulation Check 12

Participants in the operable tumor condition will recommend release less frequently compared to those in the inoperable tumor condition.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in recommended outcome, for Scenario (operable vs. inoperable).

```{r}
darley_mc12_meta
```

## Forest Plot

```{r}
darley_mc12_forest
```
