---
title: "Results of Replications of Serota et al (2010, Study 3)"
author: "Many Legal Labs"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file, encoding = encoding, output_dir = "./reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Overview

# Descriptive statistics

## Mean Lies per Day

Serota et al (2010, Study 1) found that people told on average M = 1.65, 95% CI [1.37, 1.93] lies per day (SD = 4.45, Mdn = 0, Mode = 0, N = 998, Max = 53 lies).

Study 3 found that students told an average of M = 2.34, 95% CI [1.95, 2.72] lies per day (SD = 2.94, Mdn = 1, Mode = 0, N = 225, Max = 21 lies).

We will calculate the weighted average of the mean lies told per day in each of the replication studies.

```{r}
serota_mean_meta
```

### Forest plot

```{r}
serota_mean_forest
```

## Standard Deviation of Lies per Day

```{r}
serota_sd_meta
```

# Hypothesis 1

The distribution of the number of lies told in the last 24 hours can be characterized by a power function with a negative exponent.

## Meta-analysis of Replications

This hypothesis is tested using coefficients (i.e., exponent in a power function) for a non-linear least squares regression predicting frequency from the number of lies.

```{r}
serota_h1_meta
```

## Forest Plot

```{r}
serota_h1_forest
```

# Moderator Analysis

## US compared to non-US countries

We will examine whether the United States differs from other countries with regard to the power function that characterizes the distribution of lies told per day.

We will assess whether the US differs from other countries using a Q test.

```{r}
list(Q = serota_usa_QM, p = serota_usa_QMp)
```

We will also examine each country

```{r}
serota_usa_meta
```

## Individual Countries

We will examine whether the country in which the data were collected moderates the power function that characterizes the distribution of lies told per day.

We will assess the moderating effect of country using a Q test.

```{r}
list(Q = serota_country_QM, p = serota_country_QMp)
```

We will also examine the effect size estimates for each country.

```{r}
serota_country_meta
```

