---
title: "Results of Replications of Darley et al (2000, Study 2)"
author: "Many Legal Labs"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file, encoding = encoding, output_dir = "./reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Run all necessary scripts

source("./scripts/simulate/darley_simulation.R") # REPLACE WITH DATA IMPORTATION
source("./scripts/wrangle/darley_prelim.R")
source("./scripts/calculate/darley_core.R")
source("./scripts/analyze/darley_analysis.R")

```

# Overview

# Hypothesis 1

Participants will recommend higher punishment when the perpetrator acted in a jealous rage, compared to when the behavior was caused by an inoperable tumor.

## Meta-analysis of Replications

This hypothesis will be tested using standardized mean differences for punishment recommendation, for jealous rage vs. inoperable tumor.

```{r}
darley_h1_meta
```

## Forest Plot

```{r}
darley_h1_forest
```

# Hypothesis 2

Participants will recommend higher punishment when the perpetrator acted in a jealous rage, compared to when the behavior was caused by an operable tumor.

## Meta-analysis of Replications

This hypothesis will be tested using standardized mean differences for punishment recommendation, for jealous rage vs. operable tumor.

```{r}
darley_h2_meta
```

## Forest Plot

```{r}
darley_h2_forest
```

# Hypothesis 3

Participants will recommend higher punishment when the perpetrator acted because of an inoperable tumor, compared to when the behavior was caused by an operable tumor.

## Meta-analysis of Replications

This hypothesis will be tested using standardized mean differences for punishment recommendation, for operable tumor vs. inoperable tumor

```{r}
darley_h3_meta
```

## Forest Plot

```{r}
darley_h3_forest
```

# Manipulation Check 1

Participants will attribute responsibility to the actor more frequently in the jealous rage condition, compared to when the behavior was caused by an inoperable tumor.

## Meta-analysis of Replications

We will assess this manipulation check with proportion differences (odds ratios) in attributing responsibility to the actor, for Scenario (jealous rage vs. inoperable and operable).

```{r}
darley_mc1_meta
```

## Forest Plot

```{r}
darley_mc1_forest
```

# Manipulation Check 2

Participants will attribute responsibility to the actor more frequently in the jealous rage condition, compared to when the behavior was caused by an inoperable tumor.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in attributing responsibility to the actor, for Scenario (jealous rage vs. operable).

```{r}
darley_mc2_meta
```

## Forest Plot

```{r}
darley_mc2_forest
```

# Manipulation Check 3

Participants will attribute responsibility to the actor more frequently in the inoperable tumor condition compared to the operable tumor condition.

Darley et al. found a nonsignificant difference for this comparison, but the direction of proportions was such that more people attributed responsibility to the actor when the tumor was inoperable.

## Meta-analysis of Replications

This manipulation check will be assessed using proportion differences (odds ratios) in attributing responsibility to the actor, for Scenario (operable vs. inoperable).

```{r}
darley_mc3_meta
```

## Forest Plot

```{r}
darley_mc3_forest
```
