---
title: "Results of Replications of Serota et al (2010, Study 3)"
author: "Many Legal Labs"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file, encoding = encoding, output_dir = "./reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Run all necessary scripts

source("./scripts/simulate/serota_simulation.R") # REPLACE WITH DATA IMPORTATION
source("./scripts/wrangle/serota_prelim.R")
source("./scripts/calculate/serota_core.R")
source("./scripts/analyze/serota_analysis.R")

```

# Overview

# Descriptive statistics

## Original

## Replications

# Hypothesis 1

The distribution of the number of lies told in the last 24 hours can be characterized by a power function with a negative exponent.

## Meta-analysis of Replications

This hypothesis is tested using coefficients (i.e., exponent in a power function) for a non-linear least squares regression predicting frequency from the number of lies.

```{r}
serota_h1_meta
```

## Forest Plot

```{r}
serota_h1_forest
```
