---
title: "Results of Replications of Correll et al (2002, Study 1)"
author: "Many Legal Labs"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
knit: (function(input_file, encoding) {
    rmarkdown::render(input_file, encoding = encoding, output_dir = "./reports/")
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Overview

# Hypothesis 1

Participants are faster at making a correct decision to shoot, when the target holds a gun, than the correct decision to not shoot, when the target does not hold a gun.

## Meta-analysis of Replications

This hypothesis is tested using standardized mean differences in Mean Response Latency for Object Type, across Race. The effect sizes for each replication are meta-analyzed using a random effects model.

```{r}
correll_h1_meta
```

## Forest Plot

```{r}
correll_h1_forest
```

# Hypothesis 2

Participants are faster to fire at an armed target if the target is African American than if the target is White.

## Meta-analysis of Replications

This hypothesis is tested using standardized mean differences in Mean Response Latency for Race, for Gun trials. The effect sizes for each replication are meta-analyzed using a random effects model.

```{r}
correll_h2_meta
```

## Forest Plot

```{r}
correll_h2_forest
```

# Hypothesis 3

Participants are faster to not fire at an unarmed target if the target is White than if the target is African American.

## Meta-analysis of Replications

This hypothesis is tested using standardized mean differences in Mean Response Latency for Race, for No-Gun trials. The effect sizes for each replication are meta-analyzed using a random effects model.

```{r}
correll_h3_meta
```

## Forest Plot

```{r}
correll_h3_forest
```

# Hypothesis 4

Participants are more likely to shoot an unarmed target (i.e., false alarms) than to not-shoot an armed target (i.e., misses).

## Meta-analysis of Replications

This hypothesis is tested using standardized mean differences in Errors for Object Type, across Race. The effect sizes for each replication are meta-analyzed using a random effects model.

```{r}
correll_h4_meta
```

## Forest Plot

```{r}
correll_h4_forest
```
